---
title: "Lab 04 Replication Notebook"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This is the replication notebook for Lab-04 from the course SOC 4650/5650: Introduction to GISc. 

## Load Dependencies
The following code loads the package dependencies for our analysis:

```{r package-load}
# tidyverse
library(ggplot2) # data plotting

# other packages
library(here) # working directory tools
library(sf) # spatial data tools
library(viridis) # color palettes
```

## Load Data
The following code loads the data package and assigns our data to a data frame in our global environment:

```{r data-load}
jeffTracts <- st_read(here("data","MO_DEMOS_JeffCityRegion","MO_DEMOS_JeffCityRegion.shp"), 
                      stringsAsFactors = FALSE)
```

## Create a County Population Map in `R`
### Question 10
The following code creates the map itself:

```{r jeff-plot}
ggplot() +
  geom_sf(data = jeffTracts, mapping = aes(fill = totalPopE/SQKM), color = "#5d5d5d") +
  scale_fill_viridis(option = "plasma")
```

### Question 11

This code block saves the map to the `results` subfolder:

```{r save-jeff-plot}
ggsave(here("results","lab-04-countyMap-R.png"), dpi = 300)
```

